Covariate analysis of CMC RNASeq data reprocessed with Star-Feature counts pipeline (ACC and DLPFC with TMM normlaisation)

### 2016-11-09 code/Rmd/CMC_ACC_And_DLPFC_StarAligned_TMM.Rmd
Added enrichment analysis

@@

# Store differential expression results
write.table(DE, file = 'CMC_ACC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('CMC_ACC_DiffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
stopCluster(cl)
```
|  *Results*                |  *SynapseID*                     |
|  -------                  |   ---------                      |
|  Covariates               |  `r COV_OBJ$properties$id`       |
|  Raw counts (log CPM)     |  `r COUNT_OBJ$properties$id`     |
|  Design Matrix            |  `r DM_OBJ$properties$id`        |
|  Residual Expression      |  `r EXP_OBJ$properties$id`       |
  |  Differential Expression  |  `r DEXP_OBJ$properties$id`      |

>>>>

### Gene set enrichment analysis
Using Fisher's exact test for gene set enrichment analysis
```{r enrich.de, fig.height=16, fig.width=16}
diffexp.genes = DE %>%
  dlply(.(Comparison, Tissue), .fun = function(x){
    tmp = x$hgnc_symbol[x$adj.P.Val <= 0.05] %>% unique
    tmp = tmp[!is.na(tmp)]
  })
diffexp.genes = diffexp.genes[sapply(diffexp.genes, length) > 20]
backgroundGenes = unique(DE$hgnc_symbol)

# Download all related genesets from synapse
geneset.files = synQuery('select * from file where parentId == "syn3240583"')
ALL_USED_IDs = c(ALL_USED_IDs, geneset.files$file.id)
genesets.to.test = sapply(geneset.files$file.id, function(id){
  tmp = downloadFile(id) %>%
    dlply(.(Name), .fun = function(x){
      str_split(x$symBeforeOverlap, '\\|') %>% unlist %>% unique
    })
  }) %>%
  CovariateAnalysis::filterGeneSets(backgroundGenes) %>%
  do.call(c,.)

# Perform enrichment analysis
enrich.Results = llply(diffexp.genes, .fun = function(x, genesetsToTest, backgroundGenes){
   ldply(genesetsToTest, .fun = function(y,x,backgroundGenes){
     CovariateAnalysis::fisherEnrichment(x, y, backgroundGenes)
    }, x, backgroundGenes, .parallel = TRUE) %>%
    dplyr::mutate(fdr = p.adjust(pval, method = 'fdr'))
}, genesets.to.test, backgroundGenes) %>%
  rbindlist(idcol = 'Comparison', use.names = T, fill = T)
```

@@

# Store differential expression results
write.table(DE, file = 'CMC_ACC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('CMC_ACC_DiffExpression.tsv', name = 'Differential Expression Analysis', parentId = CODE$properties$id)
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)

# Store results of enrichment analysis
write.table(enrich.Results, file = 'CMC_DLPFC_ACC_Enrichment.tsv', sep = '\t', row.names=F, quote=F)
ENR_OBJ = File('CMC_DLPFC_ACC_Enrichment.tsv', name = 'Enrichment Analysis', parentId = CODE$properties$id)
ENR_OBJ = synStore(ENR_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
stopCluster(cl)
```
|  *Results*                |  *SynapseID*                     |
|  -------                  |   ---------                      |
|  Covariates               |  `r COV_OBJ$properties$id`       |
|  Raw counts (log CPM)     |  `r COUNT_OBJ$properties$id`     |
|  Design Matrix            |  `r DM_OBJ$properties$id`        |
|  Residual Expression      |  `r EXP_OBJ$properties$id`       |
|  Differential Expression  |  `r DEXP_OBJ$properties$id`      |
